With Great Growth, Comes Greater Consumption: Energy Consumption of Countries Around the world in Relation to Their annual GDP growth

### 2024-04-22 paper/paper.qmd
Update paper, clean up files

---
title: "With Great Growth, Comes Greater Consumption: Energy Consumption of Countries Around the world in Relation to Their annual GDP growth"
subtitle: "An analysis of economic growth and energy consumption globally between 1992 to 2022"
author: 
  - Rayan Awad Alim
thanks: "Code and data are available at: https://github.com/RayanAlim/Energy-Analysis"
date: today
date-format: long
abstract: "This study explores the relationship between energy consumption and GDP growth across various income levels from 1992 to 2022 using a linear regression model. By integrating global data on energy usage in terawatt-hours and economic performance, preliminary results suggest a positive correlation between increased energy consumption and GDP growth, particularly in lower-income countries driven by industrialization. In contrast, high-income regions exhibit a nuanced relationship, possibly due to advanced energy efficiencies and shifts towards service-oriented economies. These findings emphasize the need for energy-aware economic policies that align with sustainable development goals, highlighting differentiated strategies for income groups in the face of global environmental challenges"
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

@@

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- TBD

@@

7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- TBD
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- The data is publicly available in these 2 sites https://data.worldbank.org/indicator/NY.GDP.MKTP.KD.ZG?end=2022&start=2022&view=map

9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- TBD
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- TBD
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
12. *Any other comments?*
	- TBD

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD

@@

# Model details {#sec-model-details}

>>>>

---
title: "With Great Growth, Comes Greater Consumption: Energy Consumption of Countries Around the world in Relation to Their annual GDP growth"
subtitle: "An analysis of economic growth and energy consumption globally between 1992 to 2022"
author: 
  - Rayan Awad Alim
thanks: "Code and data are available at: [RayanAlim/Energy-GDP-Analysis](https://github.com/RayanAlim/Energy-Analysis)"
date: today
date-format: long
abstract: "This study explores the relationship between energy consumption and GDP growth across various income levels from 1992 to 2022 using a linear regression model. By integrating global data on energy usage in terawatt-hours and economic performance, preliminary results suggest a positive correlation between increased energy consumption and GDP growth, particularly in lower-income countries driven by industrialization. In contrast, high-income regions exhibit a nuanced relationship, possibly due to advanced energy efficiencies and shifts towards service-oriented economies. These findings emphasize the need for energy-aware economic policies that align with sustainable development goals, highlighting differentiated strategies for income groups in the face of global environmental challenges"
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

The analysis was carried out using the statistical programming language `R` [@citeR], using the `tidyverse`[@cite_tool_tidyverse], `here`[@cite_tool_here], `dplyr`[@cite_tool_dplyr],   and `readr`[@cite_tool_readr] packages. The figures and tables in the paper are generated using the, respectively, `ggplot2`[@cite_tool_ggplot2] and `knitr`[@cite_tool_knitr] packages. Other packages used include `kableextra`[@cite_tool_kableextra],

@@

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	-  Data was downloaded from the websites: https://data.worldbank.org/indicator/NY.GDP.MKTP.KD.ZG?end=2022&start=2022&view=bar and https://ourworldindata.org/energy#explore-data-on-energy

@@

7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data is publicly available in these 2 sites
	- https://data.worldbank.org/indicator/NY.GDP.MKTP.KD.ZG?end=2022&start=2022&view=bar 
	- https://ourworldindata.org/energy#explore-data-on-energy

8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	-   The websites state that usage is made available to the public and require no consent to use the data as long as they are cited [@citeEnergyConsumption2023]

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- The dataset initially contained 7,209 entries. Through data cleaning, entries with missing values for energy consumption or GDP growth, totaling 1,041, were removed, leaving 6,168. Subsequently, entries reporting zero energy consumption were deemed inaccurate and eliminated, amounting to 501 entries. The resulting cleaned dataset comprised 5,667 entries, suitable for analysis.

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- Yes both raw and clean files are saved as wel;l as the scripts made to clean them.

@@
